Imminent range shifts in transboundary fish stocks challenge their management under climate change

### 2021-03-29 Scripts/Manuscript.Rmd
fixed bugs

```{r toeFigure3, eval = T,  echo = F, fig.width=10, fig.height=8,fig.pos= "H", fig.cap =  "Average range shift of transboundary stocks and corresponding fishing revenue per country. Countries are coded according to different colored symbols representative of 5 distinct regions. Horizontal line separates countries above and below the 75th percentile of annual fishing revenue. Showing country names for those within the top 75th percentile projected to have an average shift within 5 years after the 2030 deadline of the Sustainable Development Agenda.}

@@

img <- readPNG("../Figures/Fig5.png")
grid.raster(img)

@@

```{r supplements, child = '../Scripts/Supplements.Rmd', eval = T}

>>>>

```{r toeFigure3, eval = T,  echo = F, fig.width=10, fig.height=8,fig.pos= "H", fig.cap =  "Average range shift of transboundary stocks and corresponding fishing revenue per country. Countries are coded according to different colored symbols representative of 5 distinct regions. Horizontal line separates countries above and below the 75th percentile of annual fishing revenue. Showing country names for those within the top 75th percentile projected to have an average shift within 5 years after the 2030 deadline of the Sustainable Development Agenda."}

@@

img <- readPNG("../Figures/Fig4.png")
grid.raster(img)

@@

```{r supplements, child = '../Scripts/Supplements.Rmd', eval = F}
